---
format: 
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
execute:
  echo: false
  warning: false
  message: false
params:
  model_name: NULL
  m_file: NULL
  m_description: NULL
  m_input_data_file: NULL
  m_pos_covariates: NULL
  n_simulations: 250
  run_spatial_chunks: true
  save_dharma_residuals: false
  save_dharma_simulations: false
  run_gam_chunk: false
  run_sdmtmb_selftest_chunk: false
  selftest_nsims: 10
  meshcutoff: 10
---

```{r setup-parameters}
# Access parameters
model_name  <- params$model_name
description <- params$m_description
model_file <- params$m_file
df_surv_file <- params$m_input_data_file
model_pos_covariates <- params$m_pos_covariates
nsims <- params$n_simulations
save_dharma_res <- params$save_dharma_residuals
save_dharma_sims <- params$save_dharma_simulations
selftest_nsims <- params$selftest_nsims
meshcutoff <- params$meshcutoff

# Default fig height value in case selftest doesnt run
fig_height_selftest <- 1
```

```{r load-libraries}
library(glmmTMB)
library(DHARMa)
library(ggOceanMaps)
library(dplyr)
library(ggplot2)
library(sf)
library(dplyr)
library(tidyr)
library(mgcv)
library(sdmTMB)
library(purrr)

src_folder_location <- "src/"

source(paste0(src_folder_location, "additional_quarto_funcs.R"))
source(paste0(src_folder_location, "Variogram_function.R"))

```

---

# Report Summary

**Model name**: `r model_name`

**Model file**: `r model_file`

**Data file**: `r df_surv_file`

**Description**: `r description`

**Number of DHARMa simulations**: `r nsims`




```{r load-model-and-compute-residuals, results = 'asis'}
df_surv <- load_object(df_surv_file)

yearly_figs_h <- length(unique(df_surv$startyear)) * 5

m <- load_object(model_file)

if ("sdmTMB" %in% class(m)){
  s_mvn <- simulate(m, nsim = nsims, type = "mle-mvn")
  Esqr <- dharma_residuals(simulated_response = s_mvn,
                           object = m,
                           return_DHARMa = TRUE)
  cat(sprintf("**Model formula**: `%s`\n\n", paste(deparse(m$formula[[1]]), collapse = " ")))
} else{
  Esqr <- simulateResiduals(fittedModel = m, n = nsims, plot = F)
}
```


This report provides comprehensive model diagnostics using DHARMa (simulation-based residuals) 
and conventional approaches. It evaluates model fit through distributional comparisons, spatial 
patterns, and covariate residual relationships.

---

```{r validate-inputs}
# ---- Helper for clean errors ----
abort_render <- function(msg) {
  stop(paste0("\n❌ QUARTO VALIDATION ERROR:\n", msg), call. = FALSE)
}

# ---- 1. Required objects exist ----
req_objs <- c("df_surv", "model_pos_covariates")

missing_objs <- req_objs[!sapply(req_objs, exists)]

if (length(missing_objs) > 0) {
  abort_render(
    paste("Missing required object(s):", paste(missing_objs, collapse = ", "))
  )
}

# ---- 3. Column existence in df_surv ----
cols_needed <- unique(c("startyear", "serialnumber", 
                        "latitudestart", "longitudestart"))

missing_cols <- setdiff(cols_needed, colnames(df_surv))

if (length(missing_cols) > 0) {
  abort_render(
    paste("df_surv is missing column(s):", paste(missing_cols, collapse = ", "))
  )
}

# ---- Passed ----
message("✅ All input checks passed")
```

# Model Summary and Basic Diagnostics

## Model Specification

```{r display-model-summary}
#| message: true
summary(m)

if ("sdmTMB" %in% class(m)){
  sanity(m)
}
```

## Conventional Residuals

Conventional residuals may be less reliable for non-normal models, but provide a quick diagnostic check.

```{r plot-conventional-residuals}
#| fig-cap: "Residuals vs fitted values with LOESS smoothing"
#| label: fig-resids-vs-fitted

if ("sdmTMB" %in% class(m)){
  conv_resids <- residuals(m, type = "mle-mvn")
} else {
  conv_resids <- residuals(m)
}

conv_fitted <- fitted(m)

df_resid <- data.frame(
  Fitted = conv_fitted,
  Residuals = conv_resids
)

ggplot(df_resid, aes(Fitted, Residuals)) +
  geom_point(alpha = 0.6, color = "grey30") +
  geom_smooth(method = "loess", se = FALSE, color = "blue") +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  theme_minimal(base_size = 13)
```

## Normal Q-Q Plot

```{r plot-conventional-qq}
#| fig-cap: "Q-Q plot of conventional residuals"
#| label: fig-qq-plot
qqnorm(conv_resids); abline(0, 1)
```

---

# DHARMa Simulation-Based Diagnostics

These plots visualize the model's posterior predictive distribution by comparing simulated 
datasets from the model to the observed data. Simulation-based residuals are more powerful 
than conventional residuals, especially for non-normal models.

## Example Observations

```{r visualize-simulated-distributions}
#| fig-cap: "Posterior predictive distributions for selected observations"
#| label: fig-simulated-dist

sims_Esqr        <- Esqr$simulatedResponse
fitted_Esqr      <- Esqr$fittedPredictedResponse
observed_Esqr    <- Esqr$observedResponse

# Select 4 rows: lowest, highest, two random positive
idx_lowest  <- which.min(observed_Esqr)
idx_highest <- which.max(observed_Esqr)
positive_indices <- setdiff(which(observed_Esqr > 0),
                            c(idx_lowest, idx_highest))
idx_random <- sample(positive_indices, 2)
selected_examples <- c(idx_lowest, idx_highest, idx_random)

# Transpose sims for selected rows
sims_df_examples <- as.data.frame(t(sims_Esqr[selected_examples, , drop = FALSE]))
colnames(sims_df_examples) <- paste0("row_", selected_examples)

# Fitted + observed values for those rows
fitted_obs_df <- data.frame(
  obs_id   = paste0("row_", selected_examples),
  fitted   = fitted_Esqr[selected_examples],
  observed = observed_Esqr[selected_examples]
)

# Long format for ggplot
sims_long <- sims_df_examples %>%
  pivot_longer(cols = everything(),
               names_to = "obs_id",
               values_to = "y_sim")

# Faceted histogram plot
ggplot(sims_long, aes(x = y_sim)) +
  geom_histogram(bins = 30, color = "green", fill = "gray") +
  geom_vline(data = fitted_obs_df,
             aes(xintercept = fitted),
             color = "red", linewidth = 1) +
  geom_vline(data = fitted_obs_df,
             aes(xintercept = observed),
             color = "blue", linewidth = 1, linetype = "dashed") +
  facet_wrap(~ obs_id, scales = "free_x", ncol = 2) +
  labs(
    title = "Simulations for selected rows",
    subtitle = "Fitted (red) and observed (blue)",
    x = "Simulated response",
    y = "Count"
  ) +
  theme_minimal(base_size = 13)

if (save_dharma_sims){
  Esqr_data <- list(sims_Esqr = sims_Esqr, fitted_Esqr = fitted_Esqr,
                    observed_Esqr = observed_Esqr)
  saveRDS(Esqr_data, 
          file = paste0(dirname(model_file),"/dharma_sims_",model_name,".rds"))
}
```

## Posterior Predictive Checks (Turing Test)

Can you spot which distribution (A, B, C, or D) represents the actual observed data?

```{r prepare-turing-test}
eg_sims <- sample(nsims, 3)

turing_letters <- c("A", "B", "C", "D")

obs_letter <- sample(turing_letters, 1)

sims_letters <- setdiff(turing_letters, obs_letter)

turing_examples <- as.data.frame(sims_Esqr[, eg_sims, drop = FALSE])

colnames(turing_examples) <- sims_letters

turing_examples[[obs_letter]] <- observed_Esqr

turing_examples <- turing_examples %>% select(sort(names(.))) %>%
  mutate(latitudestart = df_surv$latitudestart,
         longitudestart = df_surv$longitudestart,
         startyear = df_surv$startyear)

turing_long <- turing_examples %>%
  pivot_longer(all_of(turing_letters))
```

### ECDF Comparison

```{r plot-turing-ecdf-linear}
#| fig-cap: "Empirical cumulative distribution functions (linear scale)"
#| label: fig-turing-ecdf-linear

ggplot(turing_long, aes(x = value, group = name, color = name)) +
  stat_ecdf(alpha = 0.5, size = 0.5) + 
  theme_minimal(base_size = 13)
```

### ECDF with Log Transform

```{r plot-turing-ecdf-log}
#| fig-cap: "Empirical cumulative distribution functions (log scale)"
#| label: fig-turing-ecdf-log

ggplot(turing_long, aes(x = value, group = name, color = name)) +
  stat_ecdf(alpha = 0.5, size = 0.5) +
  scale_x_continuous(
      trans  = "log1p",
      name   = "Response (log1p scale)"
  ) + 
  theme_minimal(base_size = 13)
```

### Posterior Predictive Density Check

```{r plot-turing-density}
#| fig-cap: "Posterior predictive density (log-transformed)"
#| label: fig-turing-density

trans <- \(x) log(x + 0.01)
trans_name <- "log(x + 0.01)"
  
ggplot() +
  geom_density(
    data = turing_long,
    mapping = aes(x = trans(value), group = name, color = name),
    alpha = 0.1,
    fill = NA
  ) +
  labs(
    title = "Posterior Predictive Density Check",
    subtitle = paste("Transformation:", trans_name),
    x = paste("Transformed response (", trans_name, ")", sep = ""),
    y = "Density"
  ) +
  theme_minimal(base_size = 13)
```

### Boxplot Comparison

```{r plot-turing-boxplots}
#| fig-cap: "Boxplot comparison of datasets"
#| label: fig-turing-boxplots

ggplot(turing_long, aes(x = value, y = name, group = name, color = name)) +
  geom_boxplot() + 
  theme_minimal(base_size = 13) + 
  theme(legend.position = "none")
```

### Spatial Distribution Maps

```{r plot-turing-maps, fig.height=yearly_figs_h/2.3}
#| fig-cap: "Spatial distribution of datasets by year"
#| label: fig-turing-maps

basemap(data = turing_long, crs = 4326, land.col = "whitesmoke") +
  geom_point(data = turing_long,
             aes(x = longitudestart, 
                 y = latitudestart,
                 col = value), size = 2.5, alpha = 0.8) +
  scale_colour_gradientn(colours = c("blue", "turquoise","yellow","lightsalmon","red"), 
                         values = scales::rescale(quantile(turing_long$value, probs = seq(0, 1, length.out = 5)))) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "white", colour = NA)) +
  labs(color = "Value") +
  facet_wrap(vars(startyear, name), ncol = 4)
```

### Answer

**Observed data: `r obs_letter`**

## Simulated vs Observed Means

```{r plot-simulated-means}
#| fig-cap: "Distribution of simulated dataset means vs observed mean"
#| label: fig-simulated-means

sim_means <- data.frame(sim_mus = apply(sims_Esqr, 2, mean))
obs_mean <- mean(observed_Esqr)

ggplot() + 
  geom_histogram(data = sim_means, aes(x = sim_mus), fill = "gray", color = "black") +
  geom_vline(xintercept = quantile(sim_means$sim_mus, 0.5),
             color = "black", linewidth = 0.5) +
  geom_vline(xintercept = quantile(sim_means$sim_mus, 0.025),
             color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_vline(xintercept = quantile(sim_means$sim_mus, 0.975),
             color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_vline(xintercept = obs_mean,
             color = "blue", linewidth = 1, linetype = "dashed") +
  labs(x = "Dataset mean") +
  theme_minimal(base_size = 13)
```

## Simulated vs Observed Distributions

```{r plot-density-identity}
#| fig-cap: "Posterior predictive density check (identity scale)"
#| label: fig-pred-check-identity
prediction_check_density_jebyrnes(Esqr)
```

```{r plot-density-log}
#| fig-cap: "Posterior predictive density check (log scale)"
#| label: fig-pred-check-log
prediction_check_density_jebyrnes(Esqr, trans = \(x) log(x+0.01))
```

```{r plot-response-distribution}
#| fig-cap: "Response distribution comparison"
#| label: fig-response-dist
sdm_plot_response_distribution(Esqr, theme = theme_minimal())
```

### ECDF Distribution

```{r plot-ecdf-distribution}
#| fig-cap: "Empirical cumulative distribution function by year"
#| label: fig-ecdf-dist
sdm_plot_ecdf_distribution(Esqr,
                           df = df_surv,
                           year_variable = "startyear",
                           by_year = F,
                           n_sim_lines = nsims,
                           show_sim_lines = T,
                           show_envelope = F,
                           log_trans = TRUE,
                           theme = theme_minimal())
```

---

# General DHARMa Tests

```{r dharma-diagnostic-tests}
#| fig-cap: "Comprehensive DHARMa diagnostic plots"
#| label: fig-dharma-tests
testResiduals(Esqr)
```

## QQ Plot

```{r plot-uniformity-qq}
#| fig-cap: "Q-Q plot for uniformity of DHARMa residuals"
#| label: fig-dharma-qq
plotQQunif(Esqr, testUniformity = TRUE, 
           testOutliers = TRUE, testDispersion = T)
```

## Dispersion Test

```{r test-dispersion}
#| fig-cap: "Dispersion test results"
#| label: fig-dispersion-test
testDispersion(Esqr, plot=TRUE)
```

```{r plot-scaled-variance}
#| fig-cap: "Residual variance scaled by mean simulated residual variance"
#| label: fig-scaled-variance

obs_pred <- observed_Esqr - fitted_Esqr
sims_pred <- sims_Esqr - fitted_Esqr
row_vars <- apply(sims_pred, 2, var)
sc_var_obs_pred <- var(obs_pred) / mean(row_vars)
sc_vars_sims_pred <- row_vars / mean(row_vars)
sc_vars_sims_pred_df <- data.frame(x = sc_vars_sims_pred)

ggplot() +
  geom_histogram(data = sc_vars_sims_pred_df, aes(x = x), fill = "gray", color = "black", bins = 35) +
  geom_vline(xintercept = sc_var_obs_pred, color = "red", linewidth = 1) +
  labs(x = "Residual variance scaled by mean simulated residual variance",
       y = "Frequency") +
  theme_minimal(base_size = 13)
```

## Outlier Test

```{r test-outliers}
#| fig-cap: "Outlier test results"
#| label: fig-outlier-test
testOutliers(Esqr)
```

---

# DHARMa Residuals vs Fitted

## Ranked

```{r residuals-vs-fitted-ranked}
#| fig-cap: "DHARMa residuals vs fitted values (ranked)"
#| label: fig-resids-ranked
plotResiduals(Esqr)
```

## Not Ranked

```{r residuals-vs-fitted-unranked}
#| fig-cap: "DHARMa residuals vs fitted values (unranked)"
#| label: fig-resids-unranked
plotResiduals(Esqr, rank = F)
```

## Homoscedasticity Test

```{r test-homoscedasticity}
#| fig-cap: "Absolute deviation from mean (homoscedasticity test)"
#| label: fig-homoscedasticity
plotResiduals(Esqr, absoluteDeviation = T)
```

---

# Zero Inflation

```{r test-zero-inflation}
#| fig-cap: "Zero inflation test results"
#| label: fig-zero-inflation
testZeroInflation(Esqr)
```

---

# Residuals vs Covariates

Covariates may or may not be included in the model (see Report Summary for details).

Covariates plotted: `r paste(model_pos_covariates, collapse = ", ")`

```{r residuals-vs-covariates}
#| fig-cap: "Residuals vs covariates"
#| label: fig-residuals-vs-covariates

for (covar_name in model_pos_covariates) {
 
  # Get the covariate values
  covar_values <- df_surv[[covar_name]]
  
  # Test and plot based on type
  if (is.factor(covar_values)) {
    testCategorical(
      Esqr,
      catPred = covar_values
    )
    legend("bottom", # Nasty trick to show covar_name in the plot
       inset = c(-0.3),
       legend = c(covar_name),
       xpd = TRUE,
       x.intersp = 10,
       y.intersp = 1,
       adj = 2)

  } else {
    # Ranked residuals
    plotResiduals(
      Esqr,
      form = covar_values,
      rank = TRUE,
      xlab = covar_name
    )
    
    # Unranked residuals
    plotResiduals(
      Esqr,
      form = covar_values,
      rank = FALSE,
      xlab = covar_name
    )
  }
}
```


---

# Spatial Diagnostics

```{r prepare-spatial-data, eval=params$run_spatial_chunks}
df_surv <- df_surv %>% mutate(dres = residuals(Esqr),
                              fitted = fitted_Esqr,
                              observed = observed_Esqr)

# Extract coordinates and convert to sf to run morans I
zone <- floor((mean(df_surv$longitudestart) + 180) / 6) + 1
utmCRS = paste("+proj=utm +zone=",zone," ellps=WGS84 +units=km",sep='')

xy_coords <- df_surv %>% st_as_sf(coords=c("longitudestart","latitudestart"),
                                        remove=FALSE, crs="+proj=longlat +datum=WGS84") %>%
  st_transform(crs = utmCRS) %>% st_coordinates()

utm_coords <- data.frame(startyear=df_surv$startyear,serialnumber=df_surv$serialnumber,xkm=xy_coords[,1],ykm=xy_coords[,2])

df_surv_xycoords <- left_join(df_surv,utm_coords)

df_surv_sf <- df_surv_xycoords %>% st_as_sf(coords=c("xkm","ykm"),
                                               remove=FALSE, crs=utmCRS)

if (save_dharma_res){
  saveRDS(df_surv_xycoords, file = paste0(dirname(model_file),"/df_esqr_",model_name,".rds"))
}
```

## Residuals Spatial Distribution

```{r map-residuals-by-year, fig.height=yearly_figs_h, eval=params$run_spatial_chunks}
#| fig-cap: "Spatial distribution of DHARMa residuals by year"
#| label: fig-residuals-map

basemap(data = df_surv, crs = 4326, land.col = "whitesmoke") +
  geom_point(data = df_surv,
             aes(x = longitudestart, 
                 y = latitudestart,
                 col = dres), size = 2.5, alpha = 0.8) +
  scale_colour_gradientn(colours = c("blue", "turquoise","yellow","lightsalmon","red"), 
                         values = c(0, 0.2, 0.4, 0.6, 0.8, 1),
                         limits = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "white", colour = NA)) +
  labs(color = "DHARMa residuals") +
  facet_wrap(~ startyear, ncol=1)
```

## Spatial Autocorrelation

```{r plot-morans-i, eval=params$run_spatial_chunks}
#| echo: false
#| fig-cap: "Moran's I test for spatial autocorrelation by year"
#| label: fig-morans-i

res_autocor_df <- check_res_spat_autocor(df_surv_sf) %>% 
  mutate(fYear = as.factor(startyear),
         MoransI_diff = obs_MorI - exp_MorI,
         signif = ifelse(p_val < 0.05,"Yes","No"),
         p_val_r = round(p_val,2))

ggplot(res_autocor_df) +
  geom_col(aes(x=fYear, y=MoransI_diff, fill = as.factor(signif))) + 
  geom_text(aes(x=fYear, y=MoransI_diff+0.005, label = p_val_r), angle = 90, hjust = 0) +
  labs(x="", y= "Moran's I score", fill = "p value < 0.05") +
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```

## Yearly Variograms

```{r calculate-variograms, eval=params$run_spatial_chunks}
#| echo: false
#| message: false
#| warning: false
#| results: 'hide'
#| fig-show: "hide"

fitted_autovars_obj <- fit_autovars(sf_data = df_surv_sf,
                                    response_column = "dres")
```

```{r plot-yearly-variograms, eval=params$run_spatial_chunks}
#| fig-cap: "Variograms by year"
#| label: fig-yearly-variograms
plot_autovars(fitted_autovars_obj[[1]])
```

## Combined Variograms

```{r plot-combined-variograms, eval=params$run_spatial_chunks}
#| fig-cap: "Combined variogram for all years"
#| label: fig-combined-variograms

ggplot() +
  geom_point(data=fitted_autovars_obj[[2]], 
             aes(x=dist, y=gamma, col=as.factor(startyear))) +
  geom_line(data=fitted_autovars_obj[[3]], 
            aes(x=dist, y=gamma, col=as.factor(startyear))) +
  labs(x="Distance (km)", y="Semi-variance (gamma)", color="Year") +
  theme_minimal(base_size = 13)
```

## Estimated Ranges

```{r plot-spatial-ranges, eval=params$run_spatial_chunks}
#| fig-cap: "Estimated spatial correlation ranges by year and variogram model"
#| label: fig-spatial-ranges

ggplot() +
  geom_col(data=fitted_autovars_obj[[4]], 
           aes(x=as.factor(startyear), y=range, fill=model)) +
  
geom_label(data = fitted_autovars_obj[[4]],
             aes(x = as.factor(startyear),
                 y = 450,
                 label = round(range, 1)),
                 position = position_dodge(width = 0.9),
             size = 4,
             angle = 90) + 

  labs(x="", y="Spatial correlation range (km)", fill="Variogram \nmodel") + 
  coord_cartesian(ylim=c(0,500)) +
  theme_minimal(base_size = 13) +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))
```

---

# Additional Checks

```{r gam-checks, eval=params$run_gam_chunk, results='asis'}

writeLines(sprintf("\n\n## GAM Concurvity\n"))

gam.check(m)
concurvity(m, full=TRUE)
```

```{r sdmtmb-self-test-setup, eval=params$run_sdmtmb_selftest_chunk, results='asis'}

writeLines(sprintf("\n\n## sdmTMB Self-Test\n"))

writeLines(sprintf("\n\n %s\n", paste("N self testing simulations:", selftest_nsims)))

writeLines(sprintf("\n\n %s\n", paste("Mesh cutoff:", meshcutoff)))

selftest_sims <- sample(nsims, selftest_nsims)

selftest_examples <- as.data.frame(sims_Esqr[, selftest_sims, drop = FALSE])

colnames(selftest_examples) <- seq(selftest_nsims)

resp_var <- sub("^([^[:space:]]+).*", "\\1", deparse(m$formula[[1]]))

mesh <- make_mesh(df_surv, xy_cols = c("xkm", "ykm"), cutoff = meshcutoff)

selftest_results <- map_dfr(seq_len(selftest_nsims), function(i) {
  
  df_tmp <- df_surv
  df_tmp[[resp_var]] <- selftest_examples[, i]
  
  refit_m <- tryCatch({
    
    sdmTMB(
      formula = formula(m),
      data = df_tmp,
      offset = m$offset,
      mesh = mesh,
      family = m$family,
      spatial = m$spatial,
      spatiotemporal = m$spatiotemporal,
      time_varying = m$time_varying,
      time_varying_type = m$time_varying_type,
      time = "startyear",
      control = sdmTMBcontrol(
        eval.max = 5000,
        iter.max = 4000,
        nlminb_loops = 3
      )
    )
    
  }, error = function(e) {
    
    message(sprintf("Simulation %s failed: %s", i, e$message))
    return(NULL)
    
  })
  
  if (is.null(refit_m)) return(NULL)
  
  params_tmp <- bind_rows(
    tidy(refit_m),
    tidy(refit_m, effects = "ran_pars"),
    tidy(refit_m, effects = "ran_vals"),
    tidy(refit_m, effects = "ran_vcov")
  ) %>%
    mutate(sim = i)
  
  params_tmp
  
})

params_m <- bind_rows(
    tidy(m),
    tidy(m, effects = "ran_pars"),
    tidy(m, effects = "ran_vals"),
    tidy(m, effects = "ran_vcov")
  ) %>%
    mutate(sim = 0)

selftest_results <- bind_rows(selftest_results, params_m) %>% arrange(sim)

fig_height_selftest <- 5 * length(unique(selftest_results$term))
```

```{r plot-selftest-results, eval=params$run_sdmtmb_selftest_chunk, fig.height=fig_height_selftest}
#| fig-cap: "Parameter estimates across self-test simulations (0 = original model)"
#| label: fig-selftest-params
ggplot(selftest_results, aes(x = sim, y = estimate, color = factor(sim))) +
  geom_point() + geom_errorbar(aes(ymin = conf.low, ymax = conf.high), width = 0.2) +
  geom_hline(data = selftest_results %>% filter(sim == 0), 
    aes(yintercept = conf.low), color = "black", linetype = "dashed") +
  geom_hline(data = selftest_results %>% filter(sim == 0), 
  aes(yintercept = conf.high), color = "black", linetype = "dashed") +
  scale_x_discrete() +
  labs(x = "", y = "Estimate", color = "Simulation (0 = original)",
  title = "Self-test results") +
  theme_minimal(base_size = 13) + 
  facet_wrap(~ term, scales = "free_y", ncol = 1) +
  theme(legend.position = "top")
```

---

*Report generated on `r Sys.time()`*
