---
format: 
  html:
    embed-resources: true
    theme: cosmo
    toc: true
    toc-depth: 3
    toc-expand: true
execute:
  echo: false
  warning: false
  message: false
params:
  model_name: NULL
  m_file: NULL
  m_description: NULL
  m_input_data_file: NULL
  m_pos_covariates: NULL
  n_simulations: 250
  run_spatial_chunks: true
  save_dharma_residuals: false
  save_dharma_simulations: false
  run_gam_chunk: false
---



```{r params}
# Access parameters
model_name  <- params$model_name
description <- params$m_description
model_file <- params$m_file
df_surv_file <- params$m_input_data_file
model_pos_covariates <- params$m_pos_covariates
nsims <- params$n_simulations
save_dharma_res <- params$save_dharma_residuals
save_dharma_sims <- params$save_dharma_simulations

cat("Model:", model_name, "\n")
cat("Model file:", model_file, "\n")
cat("Survey data file:", df_surv_file, "\n")
cat("Description:", description, "\n")

```

```{r load_packages}
library(glmmTMB)
library(DHARMa)
library(ggOceanMaps)
library(dplyr)
library(ggplot2)
library(sf)
library(dplyr)
library(tidyr)
library(mgcv)
library(sdmTMB)

src_folder_location <- "src/"
source(paste0(src_folder_location, "additional_quarto_funcs.R"))
source(paste0(src_folder_location, "Variogram_function.R"))

```

```{r collect_model}
df_surv <- load_object(df_surv_file)

yearly_figs_h <- length(unique(df_surv$startyear)) * 5

m <- load_object(model_file)

if ("sdmTMB" %in% class(m)){
  s_mvn <- simulate(m, nsim = nsims, type = "mle-mvn")
  Esqr <- dharma_residuals(simulated_response = s_mvn,
                           object = m,
                           return_DHARMa = TRUE)
  print(paste0("Formula: ", as.character(m$formula)))
} else{
  Esqr <- simulateResiduals(fittedModel = m, n = nsims, plot = F)
}
```



```{r input_validation}
# ---- Helper for clean errors ----
abort_render <- function(msg) {
  stop(paste0("\n❌ QUARTO VALIDATION ERROR:\n", msg), call. = FALSE)
}

# ---- 1. Required objects exist ----
req_objs <- c("df_surv", "model_pos_covariates")

missing_objs <- req_objs[!sapply(req_objs, exists)]

if (length(missing_objs) > 0) {
  abort_render(
    paste("Missing required object(s):", paste(missing_objs, collapse = ", "))
  )
}

# ---- 3. Column existence in df_surv ----
cols_needed <- unique(c("startyear", "serialnumber", 
                        "latitudestart", "longitudestart"))

missing_cols <- setdiff(cols_needed, colnames(df_surv))

if (length(missing_cols) > 0) {
  abort_render(
    paste("df_surv is missing column(s):", paste(missing_cols, collapse = ", "))
  )
}

# ---- Passed ----
message("✅ All input checks passed")
```



# Model Summary

```{r modelsummary}
#| message: true
summary(m)

if ("sdmTMB" %in% class(m)){
  sanity(m)
}
```

# Conventional residuals()

```{r conventionalresiduals}

if ("sdmTMB" %in% class(m)){
  conv_resids <- residuals(m, type = "mle-mvn")
} else {
  conv_resids <- residuals(m)
}

conv_fitted <- fitted(m)

df_resid <- data.frame(
  Fitted = conv_fitted,
  Residuals = conv_resids
)

ggplot(df_resid, aes(Fitted, Residuals)) +
  geom_point(alpha = 0.6, color = "grey30") +
  geom_smooth(method = "loess", se = FALSE, color = "blue") +
  geom_hline(yintercept = 0, color = "red", linewidth = 1) +
  theme_minimal(base_size = 13)

```
## Normal QQ Plot
```{r conventionalqqplot}
qqnorm(conv_resids);abline(0,1)
```

# DHARMa simulations

```{r dharmaexamples}

# --- Extract the objects ---
sims_Esqr        <- Esqr$simulatedResponse          # matrix sims per obs
fitted_Esqr      <- Esqr$fittedPredictedResponse
observed_Esqr    <- Esqr$observedResponse

# --- Select 4 rows: lowest, highest, two random positive ---
idx_lowest  <- which.min(observed_Esqr)
idx_highest <- which.max(observed_Esqr)
positive_indices <- setdiff(which(observed_Esqr > 0),
                            c(idx_lowest, idx_highest))
idx_random <- sample(positive_indices, 2)
selected_examples <- c(idx_lowest, idx_highest, idx_random)

# --- Transpose sims for selected rows ---
sims_df_examples <- as.data.frame(t(sims_Esqr[selected_examples, , drop = FALSE]))
colnames(sims_df_examples) <- paste0("row_", selected_examples)

# --- Fitted + observed values for those rows ---
fitted_obs_df <- data.frame(
  obs_id   = paste0("row_", selected_examples),
  fitted   = fitted_Esqr[selected_examples],
  observed = observed_Esqr[selected_examples]
)

# --- Long format for ggplot ---
sims_long <- sims_df_examples %>%
  pivot_longer(cols = everything(),
               names_to = "obs_id",
               values_to = "y_sim")

# --- Faceted histogram plot ---
ggplot(sims_long, aes(x = y_sim)) +
  geom_histogram(bins = 30, color = "green", fill = "gray") +
  
  # Fitted prediction (red)
  geom_vline(data = fitted_obs_df,
             aes(xintercept = fitted),
             color = "red", linewidth = 1) +
  
  # Observed value (blue dashed)
  geom_vline(data = fitted_obs_df,
             aes(xintercept = observed),
             color = "blue", linewidth = 1, linetype = "dashed") +
  
  facet_wrap(~ obs_id, scales = "free_x", ncol = 2) +
  labs(
    title = "DHARMa simulations: fitted (red) and observed (blue) for selected rows",
    x = "Simulated response",
    y = "Count"
  ) +
  theme_minimal(base_size = 13)

if (save_dharma_sims){
  Esqr_data <- list(sims_Esqr = sims_Esqr, fitted_Esqr = fitted_Esqr,
                    observed_Esqr = observed_Esqr)
  saveRDS(Esqr_data, 
          file = paste0(dirname(model_file),"/dharma_sims_",model_name,".rds"))
}

```

## Simulation means

```{r dharmasimmeans}

sim_means <- data.frame(sim_mus = apply(sims_Esqr,2,mean))
obs_mean <- mean(observed_Esqr)
fitted_mean <- mean(fitted_Esqr)

ggplot() + 
  geom_histogram(data=sim_means, aes(x=sim_mus), fill="gray", color="black") +
  geom_vline(xintercept = quantile(sim_means$sim_mus,0.5),
             color = "black", linewidth = 0.5) +
  geom_vline(xintercept = quantile(sim_means$sim_mus,0.025),
             color = "black", linewidth = 0.5, linetype = "dashed") +
  geom_vline(xintercept = quantile(sim_means$sim_mus,0.975),
             color = "black", linewidth = 0.5, linetype = "dashed") +
  
  # Fitted prediction (red)
  geom_vline(xintercept = fitted_mean,
             color = "red", linewidth = 1) +
  
  # Observed value (blue dashed)
  geom_vline(xintercept = obs_mean,
             color = "blue", linewidth = 1, linetype = "dashed") +
  labs(x="Dataset mean") +
  theme_minimal()


```

# Simulated vs Observed distributions

```{r simvsobsdistributions}

sdm_plot_response_distribution(Esqr, theme = theme_minimal())

```

# Simulated vs Observed ECDFs

```{r ecdfs}

sdm_plot_ecdf_distribution(Esqr,
                           df = df_surv,
                           year_variable = "startyear",
                           by_year   = F,
                           n_sim_lines   = nsims,
                           show_sim_lines = T,
                           show_envelope  = F,
                           log_trans = TRUE,
                           theme     = theme_minimal())


```



# General DHARMa plots

```{r dharmatestresidualsplot}
testResiduals(Esqr)

```
## QQ plot

```{r qqplot}
plotQQunif(Esqr, testUniformity = TRUE, 
           testOutliers = TRUE, testDispersion = T)
```


## Dispersion test

```{r dispersiontest}
testDispersion(Esqr, plot=TRUE)
```

```{r manualdispersionplot}

obs_pred <- observed_Esqr-fitted_Esqr

sims_pred <- sims_Esqr-fitted_Esqr

row_vars <- apply(sims_pred, 2, var)

sc_var_obs_pred <- var(obs_pred)/mean(row_vars)

sc_vars_sims_pred <- row_vars/mean(row_vars)

sc_vars_sims_pred_df <- data.frame(x=sc_vars_sims_pred)

ggplot() +
  geom_histogram(data=sc_vars_sims_pred_df ,aes(x=x), fill="gray", color="black", bins=35) +
  geom_vline(xintercept = sc_var_obs_pred, color="red", linewidth = 1) +
  labs(x="Residual variance scaled by mean simulated residual variance",
       y="Frequency") +
  theme_minimal()
```


## Outlier test

```{r outliertest}
testOutliers(Esqr)
```

# DHARMA residuals vs predicted

## Ranked

```{r residsvspredsranked}
plotResiduals(Esqr) 
```

## Not ranked

```{r residsvspredsnotranked}
plotResiduals(Esqr, rank = F) 
```

## Homoscedasticity test

```{r absdevtest}
plotResiduals(Esqr, absoluteDeviation = T) 
```

# Zero Inflation

```{r zeroinflation}
testZeroInflation(Esqr)
```



# Residuals against covariates
Covariates may or may not be included in the model (go to model summary to check).

```{r residsagainstcovs, results='asis'}


for (covar_name in model_pos_covariates) {

  # pull the variable from the dataset
  covar_values <- df_surv[[covar_name]]

  # print a true Quarto subheader (must use writeLines + results='asis')
  writeLines(sprintf("\n\n## %s\n", covar_name))

  if (is.factor(covar_values)) {

    # factor version: DHARMa rewrites axis, so use mtext()
    testCategorical(
      Esqr,
      catPred = covar_values
    )

  } else {

    # numeric version — ranked
    plotResiduals(
      Esqr,
      form = covar_values,
      rank = TRUE,
      xlab = covar_name
    )

    # numeric version — unranked
    plotResiduals(
      Esqr,
      form = covar_values,
      rank = FALSE,
      xlab = covar_name
    )
  }
}

```

# Spatial diagnostics

```{r spatialsetup, eval=params$run_spatial_chunks}
df_surv <- df_surv %>% mutate(dres = residuals(Esqr),
                              fitted = fitted_Esqr,
                              observed = observed_Esqr)

# Extract coordinates and convert to sf to run morans I
zone <- floor((mean(df_surv$longitudestart) + 180) / 6) + 1
utmCRS = paste("+proj=utm +zone=",zone," ellps=WGS84 +units=km",sep='')

xy_coords <- df_surv %>% st_as_sf(coords=c("longitudestart","latitudestart"),
                                        remove=FALSE, crs="+proj=longlat +datum=WGS84") %>%
  st_transform(crs = utmCRS) %>% st_coordinates()

utm_coords <- data.frame(startyear=df_surv$startyear,serialnumber=df_surv$serialnumber,xkm=xy_coords[,1],ykm=xy_coords[,2])

df_surv_xycoords <- left_join(df_surv,utm_coords)

df_surv_sf <- df_surv_xycoords %>% st_as_sf(coords=c("xkm","ykm"),
                                               remove=FALSE, crs=utmCRS)

if (save_dharma_res){
  saveRDS(df_surv_xycoords, file = paste0(dirname(model_file),"/df_esqr_",model_name,".rds"))
}
```




## Residuals spatial distribution

```{r resspatialdistr, fig.height=yearly_figs_h, eval=params$run_spatial_chunks}

basemap(data = df_surv, crs = 4326, land.col = "whitesmoke") +
  geom_point(data = df_surv,
             aes(x = longitudestart, 
                 y = latitudestart,
                 col = dres),size = 2.5, alpha = 0.8)  +
  
  scale_colour_gradientn(colours = c("blue", "turquoise","yellow","lightsalmon" ,"red"), 
                         values = c(0, 0.2, 0.4, 0.6, 0.8, 1),
                         limits = c(0, 1)) +
  theme_minimal() +
  theme(legend.position = "bottom",
        panel.background = element_rect(fill = "white", colour = NA)
        
  ) +
  labs(color="DHARMa residuals") +
  facet_wrap(~ startyear, ncol=1)

```

## Spatial autocorrelation

```{r spatialautocorrelation, eval=params$run_spatial_chunks}
#| echo: false
#| message: false
#| warning: false
#| results: 'hide'

res_autocor_df <- check_res_spat_autocor(df_surv_sf) %>% 
  mutate(fYear = as.factor(startyear),
         MoransI_diff = obs_MorI - exp_MorI,
         signif = ifelse(p_val < 0.05,"Yes","No"),
         p_val_r = round(p_val,2))

ggplot(res_autocor_df) +
  geom_col(aes(x=fYear, y=MoransI_diff, fill = as.factor(signif))) + 
  geom_text(aes(x=fYear, y=MoransI_diff+0.005, label = p_val_r), angle = 90, hjust = 0) +
  labs(x="", y= "Moran's I score", fill = "p value < 0.05") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))

```

## Yearly variograms

```{r variogramscalculations, eval=params$run_spatial_chunks}
#| echo: false
#| message: false
#| warning: false
#| results: 'hide'
#| fig.show: "hide"

fitted_autovars_obj <- fit_autovars(sf_data =  df_surv_sf,
                                    response_column = "dres")
```


```{r variogramsplots, eval=params$run_spatial_chunks}
plot_autovars(fitted_autovars_obj[[1]])
```

## Combined variograms

```{r variogramsplotcombined, eval=params$run_spatial_chunks}

ggplot() +
  geom_point(data=fitted_autovars_obj[[2]], 
             aes(x=dist, y=gamma, col=as.factor(startyear))) +
  
  geom_line(data=fitted_autovars_obj[[3]], 
            aes(x=dist, y=gamma, col=as.factor(startyear))) +
  
  labs(x="Distance (km)", y="Semi-variance (gamma)", color="") +
  #coord_cartesian(ylim = c(0,0.15)) + # If some year goes crazy
  theme_minimal()

```

## Estimated ranges

```{r rangesplot, eval=params$run_spatial_chunks}

ggplot() +
  
  geom_col(data=fitted_autovars_obj[[4]], 
             aes(x=as.factor(startyear), y=range, fill=model)) +
  
  labs(x="", y="Spatial correlation range (km)", fill="Variogram \nmodel") + 
  coord_cartesian(ylim=c(0,500)) +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = -45, hjust = 0))

```


# Model specific diagnostics 

```{r gamcheck, eval=params$run_gam_chunk}
gam.check(m)
concurvity(m, full=TRUE)
```

